\documentclass[letterpaper,12pt,notitlepage,fleqn]{article}

\usepackage{nopageno} %gets rid of page numbers
\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}
\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}
\usepackage{geometry}
\geometry{textheight=9in, textwidth=6.5in} %sets 1" margins 
\newcommand{\cred}[1]{{\color{red}#1}} %command to change font to red
\newcommand{\cblue}[1]{{\color{blue}#1}} % ...blue
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{amsmath}
\usepackage[usestackEOL]{stackengine}
\usepackage{multicol}

\def\name{Sam Quinn}

\parindent = 0.0 in
\parskip = 0.2 in

\title{Homework \#2}
\author{Sam Quinn}

\begin{document}
\maketitle
\hrule

\section{}
\textbf{Which of the following are negligible functions? Justify your answers.}
\begin{itemize}
	\item $\sqrt{\frac{\lambda}{2^{\lambda}}} \rightarrow 0$ - This happens because the denominator increases exponentialy.
	\item $\frac{1}{2^{log(\lambda^{2})}} \rightarrow 0$ - This will also approach zero as the denominator continues to grow.
	\item $\frac{1}{\lambda^{log(\lambda)}} \rightarrow 0$
	\item $\frac{1}{\lambda^{2}} \rightarrow 0$
	\item $\frac{1}{2^{(log\lambda)^{2}}} \rightarrow 0$
	\item $\frac{1}{\sqrt{\lambda}} \rightarrow \infty$
	\item $\frac{1}{2^{\sqrt{\lambda}}} \rightarrow 1$
\end{itemize}
\section{}
\textbf{Let $G:\lbrace0,1\rbrace^{\lambda} \rightarrow \lbrace0,1\rbrace^{2\lambda}$ be a length doubling PRG, and consider then algorithm $H:\lbrace0,1\rbrace^{\lambda} \rightarrow \lbrace0,1\rbrace^{3\lambda}$ given below:}
\begin{center}
\begin{multicols}{2}
\framebox{\Longstack[l]{
	$\textbf{\underline{H(s):}}$ \\
	\hspace{15pt}$x:=G(s)$ \\
	\hspace{15pt}$y:=G(0^{\lambda})$ \\
	\hspace{15pt}return $x \bigoplus y $\\
	}
}
\columnbreak
\end{multicols}
\end{center}
\section{}
\textbf{Show that $H$ is \textbf{not} a secure PRG (even if \textit{G} is). Describe a successful distinguisher for $\iota^{H}_{prg-real}$ and $\iota^{H}_{prg-rand}$. Explicitly compute its advantage.}
\begin{center}
\begin{multicols}{2}
\framebox{\Longstack[l]{
	$\textbf{\underline{H(s):}}$ \\
	\hspace{15pt}$x:=G(s)$ \\
	\hspace{15pt}return $s \Vert x $\\
	}
}
\columnbreak
\end{multicols}
\end{center}
\section{}
\textbf{Suppose $F$ is a secure PRF. Define the following function $F'$ as:\\ \\ $F'(k,x \Vert x')=F(k,x) \vert F(k,x \bigoplus x')$}\\\\
\textbf{$x$ and $x'$ are each in bits long, where in is the input length of $F$ . Show that $F'$ is \textbf{not} a secure PRF (even if $F$ is). Describe a distinguisher and compute its advantage.\\ \\
\textit{Hint:} Remember, you are not attacking $F$ . In fact, $F$ may be the best PRF in the world. You
are attacking the faulty way in which $F'$ uses $F$.}
\begin{multicols}{2}
\begin{center}
$x = 1111$ \\
$x' = 0000$ \\
$x \Vert x' = 11110000$
\end{center}
\columnbreak
$F'(k,x \Vert x')=F(k,x) \Vert F(k,x \bigoplus x')$ \\
$F'(k,x \Vert x')=1111 \Vert 1111 \bigoplus 0000$\\
$F'(k,x \Vert x')=1111 1111$
\end{multicols}
We can exploit $F'$ by taking advantage of the $\bigoplus$ with a zero string. So now if we pass in a string where the second half of the string is all $0$'s then we can prove that we will get repeating results back consistently.
	
\end{document}
