\documentclass[letterpaper,10pt,notitlepage,fleqn]{article}

\usepackage{nopageno} %gets rid of page numbers
\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}
\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}
\usepackage{geometry}
\geometry{textheight=9in, textwidth=6.5in} %sets 1" margins 
\newcommand{\cred}[1]{{\color{red}#1}} %command to change font to red
\newcommand{\cblue}[1]{{\color{blue}#1}} % ...blue
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{listings}

\def\name{Group 22}

\parindent = 0.0 in
\parskip = 0.2 in

\title{Project 2 Write Up}
\author{Group 22}

\begin{document}
\maketitle
\hrule

\section*{Our Solution}
For this project, we started by grepping through the Linux Kernel v3.0.4 for the 
noop implementation that was mentioned in the assignment. We knew it was in the 
../block folder and found the implementation to be in the noop-iosched.c file. 
Most of the functions in this C file could be kept as they were. The only changes 
we really made were to the data structure of a SSTF and the dispatch. Noop operates 
by taking the next request from a queue and then dispatching it, regardless of 
position. SSTF, or Shortest Seek Time First, behaves different since it selects 
an I/O request that is closer to its current position. As a result, we need to 
add two new variables to the SSTF data structure so that the function has 
positions to compare the values with. 

Next, we needed to heavily modify the dispatch function so that it works as a 
SSTF scheduler. Since a SSTF I/O scheduler processes I/O requests according to 
relative position of the request to the disk head there are a few more things we needed to account for. While a I/O request could 
the shortest distance from the disk head, however, if the request location is behind the disk head at the time it could be 
the slowest seek time since the disk is moving in a constant direction. Our 
algorithm takes advantage of an elevator that essentially traverses the I/O 
queue picking up new requests on its way. Once the elevator reaches the 
end it will flip direction and do the same but in reverse. After we initialize our elevator, we have 
to make sure that the queue is not empty so that we may have values to compare. 
The current position is then checked against the head and the direction that it 
is going. If it is going forward and the request is ahead of the list head, then 
only those values will be compared until the smallest absolute distance between 
the two are found. If you are going backwards, then you are only considering and 
comparing against the values behind the head. After the smallest absolute values 
is found, that I/O process is dispatched. Afterwards, the head is changed either 
to the front or bottom of the sector that it made the dispatch on for future 
dispatches. 

\section*{Work Log}

\begin{center}
    \begin{tabular}{| p{3cm} | l | l | p{5cm} |}
        \hline
        Date & Author & Commit & Summary \\ \hline
        Tue Oct 14 15:00 & Sam Quinn & 9402a8ddf13ad69b80eb9bf42c294822aff87b2f & Added the Linux folder for homework \#2.
        \\ \hline
        Fri Oct 17 13:39 & Bob & 8daeb619e3ebf201b079b3643e83c70c119f8de0 & Coppied the Noop I/) scheduler for a template in creating the new SSTF scheduler.
        \\ \hline
        Wed Oct 22 18:42 & Bob & 6fbc561c60d26ea444b063b912ac01068f5fca44 & Implemented sstf\_dispatch
        \\ \hline
        Sat Oct 25 15:22 & Bob & 3c4249ea31657ed2d5eadf9fa9e8ac52923a38d7 & Fixed case logic in SSTF\_dispatch
        \\ \hline
        Sat Oct 25 15:55 & Bob & b57104fba0b40f41f79c19d08310b543f8b7f6b9 & Added a hw2 Writeup doc.
        \\ \hline
        Sat Oct 25 21:36 & Bob & c918023c4d2f92f087e1cd721bde987b6291fe5a & Added Sam's project 2 writeup file.
        \\ \hline
        Sun Oct 26 21:57 & Bob & 4737476b348f7fb7acc3b47daa5328d41d393117 & Update sstf-iosched.c fully working.
        \\ \hline
        Mon Oct 27 02:38 & lawrencechau & 0fad02a3acef842d3d4b7ec6d4b1ebca2781cf29 & Update group\_22\_writeup.tex, Wrote the group writeup
        \\ \hline
        Mon Oct 27 11:53 & Bob & 50ea3799a520d50c9ee0f32ff3bf0f7b3b56a180 & Added the patch file with our SSTF I/O Scheduler.
        \\ \hline
        Mon Oct 27 11:55 & Bob & e06f0b76c25ebca39a0051d0132ba7c8ad74bf54 & Added the Linux Kernel source as a git ignored file.
        \\ \hline
        Mon Oct 27 11:56 & Bob & 43e34595c135bd9258a2b2ceaab1e0a069a41c8b & Added untracked files from previous concurrency problem.
        \\ \hline
    \end{tabular}
\end{center}
\end{document}
