\documentclass[letterpaper,10pt,notitlepage,fleqn]{article}

\usepackage{nopageno} %gets rid of page numbers
\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}
\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}
\usepackage{geometry}
\geometry{textheight=9in, textwidth=6.5in} %sets 1" margins 
\newcommand{\cred}[1]{{\color{red}#1}} %command to change font to red
\newcommand{\cblue}[1]{{\color{blue}#1}} % ...blue
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{listings}

\def\name{Group 22}

\parindent = 0.0 in
\parskip = 0.2 in

\title{Project 4 Write Up}
\author{Group 22}

\begin{document}
\maketitle
\hrule

\section*{Our Plan}
  To implement our best fit memory allocation algorithm we will first have to 
  understand how the current slob allocator works. After a quick search the stock 
  slob memory allocator is built with the first fit algorithm. This means that 
  the first page with that has enough room for the current memory allocation request 
  is used. Within the page the first block that can fit the requested memory is 
  also use. \\
  What we need to do is instead of jumping on the fist space available that the 
  request can fit into, we need to find the best fitting space. To find the best 
  fitting space we must first look though all of the available spaces to determine 
  which would fit the requests need the best. Once the best fit is found we then 
  allocate the memory there. One thing that we need to check for is that we are 
  checking each page for the best fit block size. 
\section*{Our Solution}
   Within the \textit{slob\_alloc()} function the first page that comes along is 
   sent to the \textit{slob\_page\_alloc()} function for allocation. We created 
   a \textit{best\_page()} function that will return the best fitting block within 
   the current page. This is used to compare each page with each other to ensure 
   that we indeed have the best fit. The \textit{best\_page()} function is essentially 
   the same as the \textit{slob\_page\_alloc()} function without the allocating 
   code.\\
   Once we have the best page within the \textit{slob\_page\_alloc()} function we 
   find the best block for the current request. We use the same loop as \textit{best\_page()} 
   function but once the end of the loop is reached it begins to allocate the memory 
   instead for just returning a number. In the case that the current block being 
   checked if it is the new best is the same size as the current request the loop 
   is short circuited because there is no better fit than the same size.\\ 
   The best fit algorithm is very slow. There are a lot of request for memory allocation 
   and each time every page has to be checked then each block within that page. 
   The only performance increase we have implemented in our algorithm is the short 
   circuit of an exact fit.
\section*{Work Log}

\begin{center}
    \begin{tabular}{| p{3cm} | l | l | p{5cm} |}
        \hline
        \textbf{Date} & \textbf{Author} & \textbf{Commit} & \textbf{Summary} \\ \hline
        Sun Nov 16 13:03 & Bob & cb489e02673be2a13b4a2ebbc13bf585aa08068f & Added project 4 directory.
        \\ \hline
       Wed Nov 19 13:46 & Sam Quinn & 800d9d0d0aa8b69d2677bd601e4d40e6cfaad4b2 & Need to do some work still on slob.c
        \\ \hline
        Thu Nov 20 13:42 & Bob & fe7d942416b0c54094a67dee2512c12ce5950038 & Think it should best fit slob should work first compile, Lets see.
        \\ \hline
        Sat Nov 22 11:13 & Bob & 91a9b3fe4cbf75fce38587c4a4243d1d912505bb & Fixed loop problem in the slob alloc where it tries to find the best page.
        \\ \hline
        Sat Nov 22 20:12 & Bob & f1531eccc1b9c35f694c6f2521c168d39fd055e7 & I think this works but need to fix some modules.
        \\ \hline
        Sun Nov 23 15:33 & Bob & 2c2974b3185917312246db0d0b93e86bc0290684 & Fixed some print statements and added some more comments.
        \\ \hline
        Sun Nov 23 20:44 & Bob & ea095bc6fb797c1caacaa52e863de4f09fc10ba7 & Fixed the memorry leak.
        \\ \hline
        Mon Nov 24 09:58 & Bob & df181b728215f052c633fcbcc955f1c75390a481 & Final version of the bestfit slob algorithim.
        \\ \hline
        Mon Nov 24 10:04 & Bob & c83a3017298cf8a6e70cce375344ca460c38d402 & Added writeup files.
        \\ \hline
    \end{tabular}
\end{center}
\end{document}


























