\documentclass[letterpaper,10pt,notitlepage,fleqn]{article}

\usepackage{nopageno} %gets rid of page numbers
\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}
\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}
\usepackage{geometry}
\geometry{textheight=9in, textwidth=6.5in} %sets 1" margins 
\newcommand{\cred}[1]{{\color{red}#1}} %command to change font to red
\newcommand{\cblue}[1]{{\color{blue}#1}} % ...blue
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{listings}

\def\name{Sam Quinn}

\parindent = 0.0 in
\parskip = 0.2 in

\title{Project 1 Write Up}
\author{Sam Quinn}

\begin{document}
\maketitle
\hrule

\section*{What do you think the main point of this assignment is?}
I think the main purpose of this assignment was to investigate the Linux kernel first hand. This was a 
good way to become familiar with the Linux kernel build process.
\section*{How did you personally approach the problem? Design decisions, algorithm, etc.}
After learning that \textbf{RR} and \textbf{FIFO} scheduling algorithms come standard in the Linux kernel 
from researching we decided to compare the version of the Linux kernel that we had to the stock Linux kernel. 
I \textit{greped} through the stock Linux kernel source code and found that the scheduling algorithms are 
contained with in the \textit{sched.c} and \textit{sched\_rt.c} I ran a \textit{diff} between the two versions and found that in 
the project 1's source code was missing a few functions that are necessary for the \textbf{RR} and \textbf{FIFO} scheduling 
algorithms. After finding that the sched files differed I created a patch file with the \textbf{RR} and \textbf{FIFO} implementation.

\section*{How did you ensure your solution was correct? Testing details, for instance.}
To verify my \textbf{RR} and \textbf{FIFO} scheduling algorithms were successfully implemented I recompiled the Linux kernel 
after applying the patch to the \textit{sched} files. Once I had the kernel built I installed the image with a unique name 
and label and booted into it. Once I was running my system on the new 3.0.4 kernel I then could issue the system call
\textit{sched\_setscheduler}. The system call was faily weird so after some research I found that there was a builtin command \textit{chrt} and you can run commands with specific prioritys and schedualing algorithims. I then used \textit{chrt} to test that the implementation was correct.
\section*{What did you learn?}
I like this project because I learned how to build the Linux kernel from scratch and how to use patch files. While 
I have built other large projects from source before I have never built such a crucial part of a system before like 
the kernel. It was also very cool to use the \textit{patch} function and create patch with \textit{diff}, a tool I use all of the time.
\end{document}
